2nd_draft

### 2020-03-16 src/2nd_draft.Rmd
EDA fulfilled, full model changed

## R Markdown
libraries
```{r, message=F, warning=F}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
require(neuralnet)
library(plotly)
```

@@

2. Test correlations between past mill rates and other features.
```{r}
# continuous variables
assessment_transform <- assessment_aggregate
## TODO: mean, log transform, etc.

for(i in colnames(assessment_transform)[4:7]){
  print(sprintf("correlation between mill rate and %s: %s.",
                i, cor(assessment_aggregate$rate, eval(parse(text=paste0("assessment_aggregate$", i))))))
  print(assessment_aggregate %>%
                   ggplot(aes(x=!!as.name(i),
                              y=rate,group=AddressAssessorMunicipalityDesc,
                              color=AddressAssessorMunicipalityDesc)) + 
                   geom_point() + 
                   ggtitle(sprintf("mill rate vs %s ", i)) + 
                   geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black"))

# categorical variables
for(i in colnames(assessment_transform)[1:3]){
  print(ggplot(assessment_aggregate, aes(x=as.factor(!!as.name(i)),y=rate, fill=as.factor(!!as.name(i)))) + 
  geom_boxplot()+ 
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none"))
}
```

3.model fitting
(i) linear model
```{r}
linear_full<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount,data=assessment_aggregate)
summary(linear_full)

library(broom)

@@

Ridge Regression
reference: https://www.pluralsight.com/guides/linear-lasso-and-ridge-regression-with-r
```{r}
library(glmnet)
library(dummies)
dummy_year<-dummy(assessment_aggregate$Year)
dummy_municipal<-dummy(assessment_aggregate$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_aggregate$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_year,dummy_taxclass,assessment_aggregate$assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax)

>>>>

## R Markdown
libraries
```{r, message=F, warning=F}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
library(broom)
library(glmnet)
library(dummies)
```

@@

2. Test correlations between past mill rates and other features.
```{r}
# ______________________________________________________________________________________________
# CONTINUS variables
assessment_transform <- assessment_aggregate

# log transformation and take avg
assessment_transform[,9] <- assessment_transform$assessTotal/assessment_transform$propertyCount
names(assessment_transform)[9] <- paste("AvgTotalAssessmentValue")

cor(assessment_transform$rate,assessment_transform$AvgTotalAssessmentValue)

assessment_transform %>%
                   ggplot(aes(x=AvgTotalAssessmentValue,
                              y=rate,group=AddressAssessorMunicipalityDesc,
                              color=AddressAssessorMunicipalityDesc)) + 
                   geom_point() + 
                   ggtitle(sprintf("mill rate vs average total assessment value")) + 
                   geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

# ______________________________________________________________________________________________
# CATEGORICAL variables
for(i in colnames(assessment_transform)[2:3]){
  print(ggplot(assessment_aggregate, aes(x=as.factor(!!as.name(i)),y=rate, fill=as.factor(!!as.name(i)))) + 
  geom_boxplot()+ 
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none"))
}

# kruskal.test
kruskal.test(assessment_transform$rate~assessment_transform$TaxClassCode,data=assessment_transform)
kruskal.test(assessment_transform$rate~assessment_transform$AddressAssessorMunicipalityDesc,data=assessment_transform)
```

3.model fitting
(i) linear model
```{r}
# based on EDA, we chose to fit model using municipality, tax class code, avg assess value
linear_full<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+AvgTotalAssessmentValue,data=assessment_transform)
summary(linear_full)

@@

Ridge Regression
reference: https://www.pluralsight.com/guides/linear-lasso-and-ridge-regression-with-r
```{r}
dummy_year<-dummy(assessment_aggregate$Year)
dummy_municipal<-dummy(assessment_aggregate$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_aggregate$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_year,dummy_taxclass,assessment_aggregate$assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax)
